---
By: 'Say-re'
Date: 'January 9th, 2023'
---

``` {r setup, include=TRUE, warning=FALSE }
library(tidyverse)
```

# Notes on general code chunk settings
  * echo - whether to show code 
  * warning - choose whether warnings are displayed
  * results - hide/show output from code
  * eval - evaluate or just print code
  * include - show/hide entire input/output from code chunk
  
``` {r echo=FALSE, warning=FALSE, results=TRUE}
# Show first entries in starwars data set
head(starwars)

# Check dimensions of data
dim(starwars)

summary(starwars)

# Plot character mass versus height
ggplot(data = starwars, aes(x = height, y = mass)) +
  geom_point(aes(colour = mass)) +
  scale_color_gradient(
    limits = c(0, 200),
    low = 'violet', 
    high = 'aquamarine') +
  xlab('Height (in)') +
  ylab('Mass (lbs)')
```

``` {r echo=TRUE, warning=FALSE, results=TRUE}
ggplot(data = starwars, aes(x = height)) +
  geom_histogram(
    colour='red',
    fill='purple',
  )
```

## Summary statistics for individual columns

``` {r include=FALSE, warning=FALSE}
# Log some columns from starwars data set
starwars$name
starwars$birth_year

# Determine height mean (Remove null values to avoid NA response)
sw_height_mean <- mean(starwars$height, na.rm = TRUE)

# Determine median
sw_height_median <- median(starwars$height, na.rm = TRUE)

# Determine variance
sw_height_variance <- var(starwars$height, na.rm = TRUE)

# Determine SD
sw_height_SD <- sd(starwars$height, na.rm = TRUE)

# Log result
sw_height_mean
sw_height_median
sw_height_variance
sw_height_SD
```

Summary of starwars height statistics:  
Mean - `r format(round(sw_height_mean, 2), nsmall = 2)` cm  
Median - `r format(round(sw_height_median, 2), nsmall = 2)` cm  
Variance - `r format(round(sw_height_variance, 2), nsmall = 2)`  
Standard Deviation - +/- `r format(round(sw_height_SD, 2), nsmall = 2)` cm
